\documentstyle[12pt]{article}
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\textwidth}{6.5in}
\setlength{\topmargin}{-.3in}
\setlength{\textheight}{9in}
\pagestyle{empty}

\begin{document}

\begin{center}
{\large Ashley Towne}
\end{center}

\vspace*{.5in}
{Diversity of thought, identity, and experience are integral parts of any
    successful group of people. Appreciating differences in peers, superiors,
    and subordinates can be a challenge, however, especially when common ground
    is difficult to find. The sum of small instances of diversity that make
    each individual unique is where disparate groups of people can find common
    ground.

    My choice to pursue engineering and science is rare at Notre Dame. In order to
    pursue my goal, I had to fight bureaucracy, adjust my academic timeline,
    and endure personal and academic costs. As a woman in STEM,
    there is some cultural bias against me, but I have been very
    fortunate that the Notre Dame community cultivates an environment of
    respect, from an institutional to an individual level.

    Notre Dame's places great emphasis on pursuing social justice both within
    the university and by reaching out to the communities around us, especially
    those who are sometimes overlooked. My choir at Notre Dame has toured
    overseas in Europe and Australia, as well as domestically in the United
    States. We build community and make connections with people from very
    different backgrounds.  Every year that we are able, we also give a concert
    in a local maximum security prison. We sing with the men there and are
    allowed time to talk to them and hear their stories. Music can break down
    walls between people who might otherwise not have much in common.

    Every individual has some small quirks that make them unique. Finding
    common quirks, whether a hobby or a similar life experience, can unite a
    disparate group of people. My experiences with people from different
    backgrounds has taught me how to find the small connections and build
    relationships on those. Connecting with others via small diversities also
    leads to a greater appreciation of the bigger diversities.
}


\end{document}
